---
title: "MATH3070_LAB6"
author: "Ishaan Rajan"
date: "10/15/2020"
output: html_document
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***

## Problem 1 (Verzani problem 5.6)
*For the `batting` (**UsingR**) data set, make parallel boxplots of the batting average (`H/AB`) for each team. Which team had the greatest median average? (Use **lattice** functions for this problem.)*

```{r, tidy=TRUE, error=TRUE}
#Plotting batting.Greatest median average was ANA
library(lattice)
batting = UsingR::batting
battingAvg = batting$H / batting$AB
bwplot(teamID ~ H/AB, data = batting)
```

## Problem 2 (Verzani problem 5.7)
*For the `mtcars` data set, produce graphics of the following using **ggplot2**:*

1. *Boxplots for miles per gallon (`mpg`) for groups defined by the number of gears (`gear`).*

```{r, tidy=TRUE, error=TRUE}
library(ggplot2)
ggplot(mtcars, aes(group = gear,y = mpg, x = gear)) + geom_boxplot()
```

3. *A scatterplot of `mpg` modeled by horsepower (`hp`). Create facets by the number of cylinders (`cyl`) and `gear`.*

```{r, tidy=TRUE, error=TRUE}
# mpg modeled by horsepower
library(ggplot2)
p = ggplot(mtcars,aes(y = mpg, x = hp)) + geom_point() + facet_grid(cyl~gear)
print(p)

```

## Problem 3
*Using the `batting` data set (UsingR), create a visualization that does the following:*

* *Plots the* rate *of intentional walks (that is, the number of intentional walks divided by the number of times a player was at bat; these are the `IBB` and `AB` variables in the data set, respectively) against the* rate *of home runs (the `HR` variable in the data set) as a scatter plot*

* *Draws a trend line for these variables*

* *Identifies and labels the outlier in the data set in these variables (easily spotted once the scatter plot is drawn)*

*(Hint: `geom`-type functions can accept data arguments and will use the data set passed rather than the default for the chart. So for the third requirement, consider adding a text layer with `geom_text(data = ..., aes(...))` where the argument passed to `data` is a subset of the data set consisting of the outlier, and `aes(...)` defines how to label that outlier.)*

```{r, tidy = TRUE, error=TRUE}
# Finds trend and outlier of batting dataset
library(UsingR)
library(ggplot2)
ggplot(batting, aes(x = HR, y = IBB/AB)) +geom_point() +geom_smooth(method = "lm") +xlab("HomeRuns") +ylab("Rate of Intentional Walks") +ggtitle("Rate of Intentional Walks and HomeRuns") + geom_text(data = subset(batting, IBB/AB > .15), aes(label = teamID))
```

## Problem 4
*Reconsider the data set from a previous project containing data about the results of 2012 Olympics. I load the data in for you below:*

```{r}
olympic2012 <- read.csv("http://introcs.cs.princeton.edu/java/data/olympic-medals2012.csv")
```

*Use any plotting system (base R, **lattice**, **ggplot2**) to create plot involving at least three variables in the `olympic2012` data set, showing a relationship not yet visualized in the lecture, the textbook, or this assignment. Explain the relationship you explored and any interesting findings. **Bonus points will be given for plots that I consider exceptionally clean, clear, and insightful, accompanied with good analyses of what you found.***

```{r, tidy=TRUE, error=TRUE}
# A plot of parallel coordinate plots.The point where a data point line intersects an axis represents the value of that variable for that data point.
library(MASS)
parcoord(olympic2012[c("Gold","Silver","Bronze")],col = olympic2012$Total)
```
