---
title: "MATH3070_LAB13"
author: "Ishaan Rajan"
date: "11/29/2020"
output: pdf_document
---



## Problem 1 (Verzani problem 8.7)
*Of the last ten times you've dropped your toast, it landed sticky-side down nine times. If these are a random sample from the $\text{Ber}(p)$ distribution, find an 80% confidence interval for $p$, the probability of the stidy side landing down. (Use `binconf()` (**Hmisc**) to compute the score interval.)*

```{r, tidy = TRUE,message=FALSE}
# Your solution here
library(Hmisc)
binconf(9,10,alpha = 0.2)

```

## Problem 2 (Verzani problem 8.10)
*A survey is taken of 250 students, and a $\hat{p}$ of 0.45 is found. The same survey is repeated with 1000 students, and the same $\hat{p}$ is found. Compare the two 95% confidence intervals. What is the relationship? Is the margin of error for the second one four times smaller? If not, how much smaller is it? (Use `binom.test()` to answer this problem.)*

```{r, tidy = TRUE,message=FALSE}
binom.test(113,250)
binom.test(450,1000)

#The data indicates that the relationship is very similar. Margin of error for test 1: about 6.3%. Margin of error for test 2 is about 3.1%. The margin of error for the second test is about 2 times smaller. 
```

## Problem 3
*For the `Melanoma` (**MASS**) data set, use `prop.test()` to find a 99% confidence interval for the difference in proportion of male and female patients with an ulcer.*

```{r, tidy = TRUE,message=FALSE}
library(MASS)

mel_split <- split(Melanoma$status, Melanoma$sex)
# Get logical vectors for whether patient died from melanoma. Group 0 is
# women and group 1 is men, and the code 1 in the data indicates death from
# melanoma
fem_death <- mel_split[["0"]] == 1
man_death <- mel_split[["1"]] == 1
# Vector containing the number of deaths for both men and women
deaths <- c(Female = sum(fem_death), Male = sum(man_death))
# Vector containing sample sizes
size <- c(Female = length(fem_death), Male = length(man_death))
deaths/size

prop.test(deaths,size,conf.level = 0.99)
```

## Problem 4 (Verzani problem 8.15)
*The `stud.recs` (**UsingR**) data set contains a sample of math SAT scores from some population in the variable `sat.m`. Find a 90% confidence interval for the mean math SAT score for this data. (Do not use `t.test(); find this confidence interval "by hand".)*

```{r, tidy = TRUE,message=FALSE}
# Your solution here
library(UsingR)
p = qnorm(0.05, lower.tail = FALSE)
xbar <- mean(stud.recs$sat.m)
sigma = sd(stud.recs$sat.m)

m = p * sigma/sqrt(length(stud.recs$sat.m))
thisCI <- c(Lower = xbar - m, Upper = xbar + m)
thisCI

#check the confidence interval we just calculated
t.test(stud.recs$sat.m,conf.level = 0.9)
#the by hand CI is correct

```

## Problem 5 (Verzani problem 8.15)
*For the `homedata` (**UsingR**) data set find 90% confidence intervals for both variables `y1970` and `y2000`, assuming the sample represents some population. Use `t.test()`, but first discuss whether the model assumptions are appropriate (include some check of the assumptions, like a Q-Q plot).*

```{r, tidy = TRUE,message=FALSE}
library(ggplot2)
library(reshape2)

data1970 = homedata$y1970
data2000 = homedata$y2000

tt1 = t.test(data1970, conf.level = 0.9)
tt2 = t.test(data1970, conf.level = 0.95)
tt3 = t.test(data1970, conf.level = 0.99)

conf_int_dat <- list(`90% CI` = as.list(tt1$conf.int), `95% CI` = as.list(tt2$conf.int), 
    `99% CI` = as.list(tt3$conf.int))

melted_cid = melt(conf_int_dat)
melted_cid

plot_conf_int_dat <- dcast(melted_cid, L1 ~ L2)
names(plot_conf_int_dat) <- c("Type", "Lower", "Upper")
plot_conf_int_dat

ggplot(plot_conf_int_dat) + geom_segment(aes(x = Lower, xend = Upper, y = Type, 
    yend = Type), size = 2) + ggtitle("y1970 Confidence Intervals")

## It's clear that larger confidence levels lead to larger intervals, as can
# be seen in this graphic

tt11 = t.test(data2000, conf.level = 0.9)
tt22 = t.test(data2000, conf.level = 0.95)
tt33 = t.test(data2000, conf.level = 0.99)

conf_int_dat <- list(`90% CI` = as.list(tt11$conf.int), `95% CI` = as.list(tt22$conf.int), 
    `99% CI` = as.list(tt33$conf.int))

melted_cid = melt(conf_int_dat)
melted_cid

plot_conf_int_dat <- dcast(melted_cid, L1 ~ L2)
names(plot_conf_int_dat) <- c("Type", "Lower", "Upper")
plot_conf_int_dat

ggplot(plot_conf_int_dat) + geom_segment(aes(x = Lower, xend = Upper, y = Type, 
    yend = Type), size = 2) + ggtitle("y2000 Confidence Intervals")

# It's clear that larger confidence levels lead to larger intervals, as can
# be seen in this graphic

```

## Problem 6 (Verzani problem 8.26)
*In determining the recommended dosage of AZT for AIDS patients, tests were done comparing efficacy for various dosages. If a low dosage is effective, then that would be recommended, as it would be less expensive and would have fewer potential side effects.*

*A test to decide whether a dosage of 1,200 mg is similar to one of 400 mg is performed on two random samples of AIDS patients. A numeric measurement of a patient's health is made, and the before-and-after differences are recorded after treatment:*

|Treatment      |   |   |   |   |    |    |    |   |   |   |
|--------------:|---|---|---|---|----|----|----|---|---|---|
| 400 mg group  | 7 | 0 | 8 | 1 | 10 | 12 | 2  | 9 | 5 | 2 |
| 1200 mg group | 2 | 1 | 5 | 1 | 5  | 7  | -1 | 8 | 7 | 3 |

*Find a 90% confidence interval for the differences of the means. What do you assume about the data?*

```{r, tidy = TRUE,message=FALSE}
mg400 = c(7,0,8,1,10,12,2,9,5,2)
mg1200 = c(2,1,5,1,5,7,-1,8,7,3)
t.test(mg400,conf.level = 0.9)
t.test(mg1200,conf.level = 0.9)

#The 400mg dose seems to be more effective, as the confidence interval includes higher numeric measurements of a patients health than the 1200mg dose. 

```

## Problem 7 (Verzani problem 8.27)
*The following data is from IQ tests for pairs of twins that were separated at birth. One twin was raised by the biological parents, the other by adoptive parents.*

| Twin pair  | 1  | 2  | 3  | 4   | 5  | 6  | 7  | 8  | 9   | 10  |
|-----------:|----|----|----|-----|----|----|----|----|-----|-----|
| Foster     | 80 | 88 | 75 | 113 | 95 | 82 | 97 | 94 | 132 | 108 |
| Biological | 90 | 91 | 79 | 97  | 97 | 82 | 87 | 94 | 131 | 115 |

*Find a 90% confidence interval for the differences of mean. What do you assume about the data? In particular, are the two samples independent?*

```{r, tidy = TRUE,message=FALSE}
frame = data.frame("Twin Pair" = c(1,2,3,4,5,6,7,8,9,10), "Foster" = c(80,88,75,113,95,82,97,94,132,108), Biological = c(90,91,79,97,97,82,87,94,131,115))

t.test(frame$Foster,conf.level = 0.9)
t.test(frame$Biological,conf.level = 0.9)

#The data shows that there really is not any relationship between by what family a separated twin was raised and the IQ level of each twin respectively due to the confidence intervals being pretty much the same. 
```
