---
title: "MATH3070_LAB5"
author: "Ishaan Rajan"
date: "10/01/2020"
output: pdf_document
---

## Problem 1 (Verzani problem 5.1)
*For the `UScereal` (**MASS**) data set, create a scatter plot of `calories` modeled by `sugars` using the `shelf` variable to create different plot characters. Add a legend to indicate the shelf number. Is there any patterns? (Use base R plotting for this problem.)*

```{r, tidy=TRUE, error=TRUE}
#Creates a scatterplot of the UScereal data set of calories modeled by sugars. 
UScereal = MASS::UScereal
#sets the plot
plot(UScereal$calories,UScereal$sugars,col = UScereal$shelf,pch = UScereal$shelf)
#sets legend
legend(325,20,c("Shelf 1", "Shelf 2", "Shelf 3"),col = 1:3,pch = 1:3)
```

## Problem 2 (Verzani problem 5.3)
*For the data set `UScereal` (**MASS**) make a pairs plot of the numeric variables. Which correlation looks larger: fat and calories or fat and sugars?*

```{r, tidy=TRUE, error=TRUE}
# A pairs plot of the numeric variables in UScereal. I make use of the dplyr package.
d = MASS::UScereal
data_num = dplyr::select_if(d, is.numeric)
pairs(data_num,col = data_num$fat)
```

## Problem 3 (Verzani problem 5.4)
*For the data set `batting` (**UsingR**) make a bubble plot of home runs hit (`HR`) modeled by hits (`H`) where the scale factor for each point is given by `sqrt(SO)/10`. Is there any story to be told by the size of the points? (You must use base R plotting for this problem.)*

```{r, tidy=TRUE, error=TRUE}
# A bubble plot of home runs modeled by hits.
library(UsingR)
plot(batting$HR ~ batting$H,data = batting, pch = 16, col=rgb(red = 0, green = 0, blue = 0, alpha = 0.250),cex = sqrt(SO)/10)
#size of dot is how often they strike out
```
