---
title: "MATH 3070 Lab Project 7"
author: "Ishaan Rajan"
date: "October 6, 2016"
output: pdf_document
---



## Problem 1 (Verzani problem 3.2)
*For the `michelson` (**MASS**) data set, produce a density plot comparing `Speed` between Experiments 1 and 2.*

```{r, tidy=TRUE, error=TRUE, message=FALSE}
# Split data, and plot the density accordingly
library(MASS)
split = with(michelson,split(Speed,Expt))
E1 = split$"1"
E2 = split$"2"
plot(density(E1),lty = 1)
lines(density(E2),lty = 2)

```

## Problem 2 (Verzani problem 3.4)
*Three students record the time spent on homework per class. Their data is:*

| Student| 1  | 2  | 3  | 4  | 5 |
|:-------|---:|---:|---:|---:|--:|
| Marsha | 25 | 0  | 45 | 90 | 0 |
| Bill   | 30 | 30 | 30 | 30 |   |
| Holly  | 15 | 0  | 90 | 0  |   |

*Use a list to store these values. Then create a boxplot to compare. (You must use `boxplot()`'s formula interface for this problem.)*

```{r, tidy=TRUE, error=TRUE,message=FALSE}
# Make a list and plot. 
homeworkTime = list(Marsha = c(25,0,45,90,0), Bill = c(30,30,30,30,NA), Holly = c(15,0,90,0,NA))
boxplot(homeworkTime)
```

## Problem 3 (Verzani problem 3.5)
*A group of nursing students take turns measuring some basic assessments. Their data is:*

|          | Temp | Pulse | Systolic | Diastolic |
|----------|------|-------|----------|-----------|
| Jackie   | 98.2 | 96    |  134     | 90        |
| Florence | 98.6 | 56    |  120     | 80        |
| Mildred  | 98.2 | 76    |  150     | 95        |

*Create a data frame of these values. Will `plot()` and `boxplot()` produce the same graphic?*

```{r, tidy=TRUE, error=TRUE,message=FALSE}
# Create a data frame and plot
frame = data.frame("Name" = c("Jackie","Florence","Mildred"), "Temp" = c(98.2,98.6,98.2), "Pulse" = c(96,56,76), "Systolic" = c(134,120,150), "Diastolic" = c(90,80,95))
boxplot(Temp ~ Pulse, data = frame)
plot(Temp ~ Pulse, data = frame)
#No, plot() and boxplot() do not produce same graphic. 
```

## Problem 4 (Verzani problem 3.8)
*The second argument to `split` can be a list of factors. The result is that all interactions (possible combinations) are used for the groups. In the `ToothGrowth` data set, growth (`len`) is measured for two types of supplements (`supp`) and three doses (`dose`). Split this `len` value into 6 groups.*

```{r, tidy=TRUE, error=TRUE,message=FALSE}
# Split the data accordingly
split(ToothGrowth$len,list(ToothGrowth$dose,ToothGrowth$supp), drop = TRUE)
```
