---
title: "MATH 3070 Lab Project 3"
author: "Ishaan Rajan"
date: "September 13, 2020"
output:
  html_document:
    toc: TRUE
---



## Problem 1 (Verzani problem 2.43)
*The `time` variable in the `nym.2002` data set (**UsingR**) contains the time to finish the 2002 New York City Marathon for a random sample of the finishers.*

1. *What percent ran the race in under 3 hours?*

```{r}
# Calculates what percentage of people ran the race in under 180 minutes
times = UsingR::nym.2002$time
range(times)
under3 = sum(times < 180) / length(times)
under3 * 100
```

2. *What is the time cutoff for the top 10%? The top 25%?*

```{r}
# Finds the top 10% and 25% times
quantile(times,.1)
quantile(times,.25)
```

3. *What time cuts off the bottom 10%?*

```{r}
# Finds the top 90% of times (bottom 10%)
quantile(times,.9)
```

## Problem 2 (Verzani problem 4.1)
*The data set `UScereal` (**MASS**) contains data on cereals sold in the United States in 1993. For this data set, answer the following questions:*

1. *How many rows does the data frame have? Columns?*

```{r}
# Determines number of rows and cols in dataset
nrow(MASS::UScereal)
ncol(MASS::UScereal)
```

2. *How many different manufacturers are included?*

```{r}
# Determines number of different manufacturers included
levels(MASS::UScereal$mfr)
length(levels(MASS::UScereal$mfr))
```

3. *How many vitamin categories are included?*

```{r}
# Determines how many vitamins are included
levels(MASS::UScereal$vitamins)
length(levels(MASS::UScereal$vitamins))
```

4. *How many cereals have a sugar level above 10?*

```{r}
# Number of cereals with a sugar level above 10
numsugar = MASS::UScereal$sugars
sum(numsugar > 10)
```

5. *What is the mean calorie value for cereals with more than 5 grams of fat? Less than or equal to 5?*

```{r}
# Mean calorie value for cereals with more than 5 grams of fat and less than/equal to 5
gramsFat = MASS::UScereal$fat
newData1 = subset(MASS::UScereal,gramsFat > 5)

newDataCals = mean(newData1$calories)
newDataCals

newData2 = subset(MASS::UScereal,gramsFat <= 5)
newDataCals = mean(newData2$calories)
newDataCals


```

6. *What is the mean calorie value for cereals on the middle shelf (2)?*

```{r}
# Mean calorie for middle shelf
newData = subset(MASS::UScereal, MASS::UScereal$shelf == 2)
mean(newData$calories)

```

## Problem 3 (Verzani problem 4.2)
*R uses lists for many purposes behind the scenes. For example, the output of `lm(mpg ~ wt, data=mtcars)` returns a list. Create this object, then answer the following:*

1. *How many components does this list have?*

```{r}
# Number of components in the linear model
length(lm(mpg ~ wt, data=mtcars))
```

2. *What are the names of the components?*

```{r}
# Names of the components
names(lm(mpg ~ wt, data=mtcars))
```

3. *What kind of data is held in the `residuals` variable?*

```{r}
# Data in residuals variable
model = lm(mpg ~ wt, data=mtcars)
typeof(model$residuals)
```

## Problem 4
*Create a data frame containing the data in the following table:*

| First    | Last      | Age |
|----------|-----------|-----|
| Marcus   | Holstein  | 23  |
| Samuel   | Adams     | 56  |
| Gus      | McPherson | 43  |
| Margaret | Olsen     | 41  |
| Zim      | Newbold   | 95  |

```{r}
# A new dataframe of the above table
data.frame("First" = c("Marcus","Samuel","Gus","Margaret","Zim"),"Last" = c("Holstein","Adams","McPherson","Olsen","Newbold"), "Age" = c(23,56,43,41,95))
```
