---
title: "MATH 3070 Lab Fall Project 2 Solutions"
author: "Ishaan Rajan"
date: "9/10/2020"
output:
  html_document:
    toc: TRUE
---


## Problem 1 (Verzani problem 2.4)
*Create the following sequences, using `:`, `seq()`, or `rep()` as appropriate:*

1. `"a" "a" "a" "a" "a" "a"`

```{r}
# The vector "a" repeated 6 times
rep(c("a"),times = 6)
```

2. `1 3 ... 99` *(the odd numbers)*

```{r}
# A series of vectors containing only odd numbers from 1 to 99
seq(1,100,by = 2)
```

3. `1 1 1 2 2 2 3 3 3`

```{r}
# Repeating each element in the vector 1,2,3 three times each
rep(c(1,2,3), each = 3)
```

## Problem 2 (Verzani problem 2.3)
*Let our small data set be* `2 5 4 10 8`.

1. *Enter this data into a data vector `x`.*

```{r}
# The vector x representing the data set 2,5,4,10,8
x = c(2,5,4,10,8)
x
```

2. *Find the square of each number.*

```{r}
# The square of each element
x
x * x
```

3. *Subtract 6 from each number.*

```{r}
# 6 subtracted from each number
x
x - 6
```

4. *Subtract 9 from each number and then square the answer.*

```{r}
# Shows each step of subtracting 0 from each element in x and them squaring the answer
x
x - 9
(x - 9) * (x - 9)
```

## Problem 3 (Verzani problem 2.25)
*Write a function `isprime()` that checks if a number $x$ is prime by dividing $x$ by all the values in $2, ..., x - 1$ then checking to see if there is a remainder of 0. The expression `a %% b` returns the remainder of `a` divided by `b`.*

```{r}
# Checks if a number is prime
isprime = function(x){
  vec = 2:(x - 1)
  
  for (val in vec){
    if(x %% val == 0){
      return("FALSE");
    }
  }
    return("TRUE")
}
isprime(11)
isprime(25)
```

***BONUS:** You do not need to check all numbers from 2 to $x - 1$ to see if a number is prime. What is the largest you would need to go for an arbitrary $x$? Create a new function, `isprime2()`, that implements this better (yet still slow) method.*

```{r}
# Your code here
```

## Problem 4 (Verzani problem 2.32)
*Fit a density estimate to the data set `pi2000` (**UsingR**). Compare with the appropriate histogram. Why might you want to add an argument like `breaks = 0:10-.5` to `hist()`? (Hint: read the documentation of `hist()` to see what setting this argument does.)*

```{r}
# Fit a density estimate to the data set pi2000
hist(UsingR::pi2000-.1, prob=TRUE)
lines(density(UsingR::pi2000))
```

## Problem 5 (Verzani problem 2.34)
*The data set `DDT` (**MASS**) contains independent measurements of the pesticide DDT on kale. Make a histogram and a boxplot of the data. From these, estimate the mean and standard deviation. Check your answers with the appropriate functions.*

```{r}
#Plots the hist and boxplot of the data and finds the mean and standard deviation
hist(MASS::DDT)
boxplot(MASS::DDT)
mean((MASS::DDT))
sd(MASS::DDT)
```
