---
title: "MATH3070_LAB4"
author: "Ishaan Rajan"
date: "9/24/2020"
output: pdf_document
---

## Problem 1 (Verzani problem 4.7)
*Use the `subset()` function to return a data frame made from the `Cars93` (**MASS**) data frame consisting only of `non-USA` cars in origin, with 4 cylinders and a maximum price of \$15,000 or less.*

```{r, tidy=TRUE,error=TRUE}
# returns a data frame consisting only of `non-USA` cars in origin, with 4 cylinders and a maximum price of $15,000 or less.
d = MASS::Cars93
subset(d,subset = Origin == 'non-USA' & Cylinders == 4 & Price <= 15.0)
```

## Problem 2 (Verzani problem 4.10)
*Find the standard deviation of each variable in the `mtcars` data set.*

```{r, tidy=TRUE, error=TRUE}
# Determines the SD of each variable in mtcars
sdeviation = c()
for(vec in mtcars){
  #In R, this is how you add to vectors. Remember how to do this!
  sdeviation = c(sdeviation,sd(vec))
}
sdeviation

#a better,faster way to do this problem is as so
sapply(mtcars, sd)

```

## Problem 3 (Verzani problem 4.11)
*Find the standard deviation for each numeric variable in `Cars93` (**MASS**).*

```{r, tidy=TRUE, error=TRUE}
# Using package dplyr. Finds SD for numeric variable
d = MASS::Cars93
data_num = dplyr::select_if(d, is.numeric)
sapply(data_num,sd)
```

## Problem 4 (Verzani problem 4.12)
*Write a function that summarizes the variables in a data frame with their name and their class (returned by `class()`). (There are many ways to do so.)*

```{r, tidy=TRUE, error=TRUE}
# A function that summarizes the variables and class in a data frame
#outputs: names of all variables, class of all variables
#getting names --> names()
#getting class --> class()
mySummary = function(dataSet){
  namesVec = names(dataSet)
  classVec = sapply(dataSet,class)
  result = data.frame("variables" = namesVec, "class" = classVec)
  print(result)
}



```

## Problem 5
*You can find data describing various statistics on 2012 Olympic participating nations such as population and medal counts in the comma-separated value file located here: `http://introcs.cs.princeton.edu/java/data/olympic-medals2012.csv` Load this dataset into R in a data frame and do the following:*

1. *Create a new data frame containing only the country's ISO code (a three-letter code for the country; USA is the United States of America, and DZA Algeria), name, population, and counts for gold, silver, and bronze. This data frame should be called `olympic2012`.*

```{r, tidy=TRUE, error=TRUE}
# Creates a new data from the the given file
data = read.csv("http://introcs.cs.princeton.edu/java/data/olympic-medals2012.csv")
olympic2012 = data.frame("ISO" = data$ISO, "Name" = data$Country.name, "Population" = data$Total.pop, "NumGold" = data$Gold,"NumSilver" = data$Silver, "NumBronze" = data$Bronze)
olympic2012


```

2. *What proportion of countries earned no medals? Answer this using `olympic2012`.*

```{r, tidy=TRUE, error=TRUE}
# Finds the proportion of countries with zero medals compared to the whole population.
totalParticipants = length(olympic2012$ISO)
sumZero = sum(olympic2012$NumGold == 0 & olympic2012$NumSilver == 0 & olympic2012$NumBronze == 0)
sumZero / totalParticipants

```
